Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-18 ms.rmd
Fixed terrestrial model. Converged but needed to exclude trait categories with too little data. Just need to be clear on that in methods

```{r setup, echo = FALSE, results="hide"}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)

@@

    # Filter out antioxidant and NAs
  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time))

>>>>

```{r knitrops, echo = FALSE, results="hide"}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)

```{r setup, echo = FALSE, results="hide"}

@@

    # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR"))
